Constraining Black Hole Growth with High-z Quasar Observations

### 2022-09-01 ms.tex
version0901; me:all revised; next: check k revision

%%%%%%%
%    Fig. 
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=160mm]{QLF_rhoz.png}
\caption{
{\it Left panel}: quasar luminosity functions at $z=6-10$. 
The solid lines denote modeled QLF produced by the best-fit parameters and the shaded regions present the $1\sigma$ spread. 
{\it Right panel}: the redshift evolution of the cumulative number density of quasars with $\Muv <-26~{\rm mag}$ in a comoving volume,
evaluated by the integration of the QLF shown in the left panel.
The evolutionary trend can be approximated as $n(\Muv<-26~{\rm mag})\propto 10^{k_{L} z}$, where $k_L \simeq -0.96$.
This result indicates rapid decline of the number of bright quasars toward higher redshifts, consistent with previous observations
\citep[red data points; see][]{2016ApJ...833..222J, 2019ApJ...884...30W}
}
\label{fig:QLF_rhoz}
\vspace{5mm}
\end{figure*}

\subsection{Quasar luminosity function}
\label{sec:qlfglf}
Next, we show our prediction of $z=6-10$ unobscured QLFs taken from the BH growth model in the left panel of Fig.~\ref{fig:QLF_rhoz}.
Similar to the BHMF, for all the redshift range, the shape of the QLF is well approximated with a double power-law function.
From higher to lower redshifts, the number density of luminous quasars increases and the bright-end of the distribution rises.
% %The model QLFs we propose give interesting prediction and will be further constrained by higher redshift quasar observations.
% \red{KI: add more explanations about the QLFs. How about the detection limits of Euclid, Roman, and others?
% Also, you could compare your results with Aaron Yung's results.}
In the right panle of Fig.~\ref{fig:QLF_rhoz}, we present the number density of luminous quasars with $\Muv <-26~{\rm mag}$ as a function of redshift.
The evolutionary trend can be fitted as $\propto 10^{k_{\rm L}z}$, where $k_{\rm L}\approx -0.97$.
Observationally, a rapid decay of the quasar number density toward higher redshifts is found by previous studies
\citep[e.g.,][]{2001AJ....122.2833F,2013ApJ...768..105M,2016ApJ...833..222J,2019ApJ...884...30W},
which show $k_{\rm L}= -0.47$ and $-0.72$ from the analysis of quasar samples at $z\simeq 3-5$ and $z\simeq 5-6$, respectively.
% Recently, a steeper decline of luminous quasar number density toward higher redshifts is proposed by \citet{2019ApJ...884...30W},
% suggesting $k_{\rm L}=-0.78$ at $6\lesssim z \lesssim 7$.
The rapid decline toward higher redshifts is characterized by the treatment of episodic natures of BH accretion with a finite value of
$\tau ~(\simeq 20~{\rm Myr})$, in order to match the statistical properties of high-$z$ quasars.
We also note that the tendency would be explained by the rarity of massive quasar-host halos at higher redshifts,
non-constant radiative efficiencies that covert the BH growth rate into the luminosity, or some combination of these effects
\citep[e.g.,][]{2010ApJ...718..231S}.
%Studies with the assumption of the close correlation of DM halo mass with central BH mass, and a constant Eddington ratio 
%interprete this rapid decline by the rarity of massive halos toward higher redshifts \citep[e.g.,][]{2010ApJ...718..231S}, 
%while another entangling factor is the radiative efficiency in converting BH growth rate to luminosity. 
%In our work, we argue that the episodical BH accretion with bursts and quiescent phases is 
%important in matching the $z\sim 6$ quasar observations, 
%and this calls consideration of the more realistic BH-galaxy coevolution in understanding the observable AGN properties.

>>>>

%%%%%%%
%    Fig. 
%%%%%%%
\begin{figure}
\centering
\includegraphics[width=85mm]{M0r8_f2QLF.png} % width=160 QLF_rhoz.png
\caption{
% {\it Left panel}: quasar luminosity functions at $z=6-10$. 
% The solid lines denote modeled QLF produced by the best-fit parameters and the shaded regions present the $1\sigma$ spread. 
% {\it Right panel}: the redshift evolution of the cumulative number density of quasars with $\Muv <-26~{\rm mag}$ in a comoving volume,
% evaluated by the integration of the QLF shown in the left panel.
% The evolutionary trend can be approximated as $n(\Muv<-26~{\rm mag})\propto 10^{k_{L} z}$, where $k_L \simeq -0.96$.
% This result indicates rapid decline of the number of bright quasars toward higher redshifts, consistent with previous observations
% \citep[red data points; see][]{2016ApJ...833..222J, 2019ApJ...884...30W}
}
\label{fig:QLF_rhoz}
\vspace{5mm}
\end{figure}

\subsection{Quasar number density evolution}
\label{sec:qlfglf}
\blue{(my revision on Fig.~\ref{fig:QLF_rhoz} description)
Next, in Fig.~\ref{fig:QLF_rhoz} we show unobscured quasar number densities at different magnitudes evolving with redshift.
Based on our best-fit parameters in the BH growth model, 
we predict the number densities evolution at $z\sim 6-10$, of quasars at $\Muv=-23$ to $-27$ mag.
We also show the quasar number densities from previous observational studies, depicting the cosmic QLF evolution from $z\sim 0-6$
\citep{2006AJ....131.2766R,2008ApJ...675...49S,2013ApJ...768..105M,2018PASJ...70S..34A,2018ApJ...869..150M,2020ApJ...904...89N}.
Peaking at $z\sim 2-3$, the quasar number densities at all magnitudes decline exponentially toward high redshifts.
A rapid decay of the quasar number density toward higher redshifts is found by previous studies
\citep[e.g.,][]{2001AJ....122.2833F,2013ApJ...768..105M,2016ApJ...833..222J,2019ApJ...884...30W},
which show $k_{\rm L}= -0.47$ and $-0.72$ from the analysis of quasar samples at $z\simeq 3-5$ and $z\simeq 5-6$, respectively.
From our theoretical prediction, the evolutionary trend of luminous quasar number density of with $\Muv <-26~{\rm mag}$ can
be fitted as $\propto 10^{k_{\rm L}z}$, where $k_{\rm L}\approx -0.97$.
The rapid decline toward higher redshifts is characterized by the treatment of episodic natures of BH accretion with a finite value of
$\tau ~(\simeq 20~{\rm Myr})$, in order to match the statistical properties of high-$z$ quasars.
We also note that the tendency would be explained by the rarity of massive quasar-host halos at higher redshifts,
non-constant radiative efficiencies that covert the BH growth rate into the luminosity, or some combination of these effects
\citep[e.g.,][]{2010ApJ...718..231S}.
}

Similar to the BHMF, for all the redshift range, the shape of the QLF is well approximated with a double power-law function.
From higher to lower redshifts, the number density of luminous quasars increases and the bright-end of the distribution rises.
% %The model QLFs we propose give interesting prediction and will be further constrained by higher redshift quasar observations.
% \red{KI: add more explanations about the QLFs. How about the detection limits of Euclid, Roman, and others?
% Also, you could compare your results with Aaron Yung's results.}
In the right panle of Fig.~\ref{fig:QLF_rhoz}, we present the number density of luminous quasars with $\Muv <-26~{\rm mag}$ as a function of redshift.
The evolutionary trend can be fitted as $\propto 10^{k_{\rm L}z}$, where $k_{\rm L}\approx -0.97$.
Observationally, a rapid decay of the quasar number density toward higher redshifts is found by previous studies
\citep[e.g.,][]{2001AJ....122.2833F,2013ApJ...768..105M,2016ApJ...833..222J,2019ApJ...884...30W},
which show $k_{\rm L}= -0.47$ and $-0.72$ from the analysis of quasar samples at $z\simeq 3-5$ and $z\simeq 5-6$, respectively.
% Recently, a steeper decline of luminous quasar number density toward higher redshifts is proposed by \citet{2019ApJ...884...30W},
% suggesting $k_{\rm L}=-0.78$ at $6\lesssim z \lesssim 7$.
The rapid decline toward higher redshifts is characterized by the treatment of episodic natures of BH accretion with a finite value of
$\tau ~(\simeq 20~{\rm Myr})$, in order to match the statistical properties of high-$z$ quasars.
We also note that the tendency would be explained by the rarity of massive quasar-host halos at higher redshifts,
non-constant radiative efficiencies that covert the BH growth rate into the luminosity, or some combination of these effects
\citep[e.g.,][]{2010ApJ...718..231S}.
%Studies with the assumption of the close correlation of DM halo mass with central BH mass, and a constant Eddington ratio 
%interprete this rapid decline by the rarity of massive halos toward higher redshifts \citep[e.g.,][]{2010ApJ...718..231S}, 
%while another entangling factor is the radiative efficiency in converting BH growth rate to luminosity. 
%In our work, we argue that the episodical BH accretion with bursts and quiescent phases is 
%important in matching the $z\sim 6$ quasar observations, 
%and this calls consideration of the more realistic BH-galaxy coevolution in understanding the observable AGN properties.
